---
title: "Topic 2: Sample Designs"
subtitle: "ENVX2001 -- Applied Statistical Methods"
author: "Januar Harianto"
# date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output:
  xaringan::moon_reader:
    css: ["default", "assets/sydney-fonts.css", "assets/sydney.css"]
    self_contained: false # if true, fonts will be stored locally
    seal: true # show a title slide with YAML information
    includes:
      in_header: "assets/mathjax-equation-numbers.html"
    nature:
      beforeInit: ["assets/macros.js", "assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9' # alternatives '16:9' or '4:3' or others e.g. 13:9
      navigation:
        scroll: false # disable slide transitions by scrolling
---

```{r, load_refs, echo=FALSE, cache=FALSE, message=FALSE}
library(RefManageR)
library(readr)
library(kableExtra)

options(knitr.kable.NA = '')

BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           cite.style = 'authoryear', 
           style = "markdown",
           hyperlink = FALSE, 
           dashed = FALSE)
myBib <- ReadBib("assets/example.bib", check = FALSE)
```

## Outline

```{r, echo=FALSE, message=FALSE}
read_csv("assets/tables/envx2001_outline.csv") %>%
  kable() %>%
  # collapse_rows(columns = 1:6, valign = "top") %>%
  kable_styling(font_size = 18) %>%
  pack_rows("Part 1: Designed Studies", 1, 6) %>%
  pack_rows("Part 2: Finding Patterns in Data", 7, 12) %>%
  pack_rows("Part 3: Revision", 13, 13) %>%
  row_spec(2, bold = TRUE, color = "darkgreen")
```


---
## Learning Outcomes

At the end of this Topic, students should be able to:

.pull-left[
- Calculate means and their uncertainty for a
  - simple random design
  - stratified random design
- Make simple recommendations for designing sampling schemes
- Demonstrate proficiency in the use of R for analysis of sample design data, for
  - estimating a mean
  - estimating a change in mean
  - choosing sample sizes
- Demonstrate proficiency in the use of R to generate sampling designs
]






---
## Learning Outcomes

At the end of this Topic, students should be able to:

.pull-left[
- **Calculate means and their uncertainty for a**
  - **simple random design**
  - **stratified random design**
- Make simple recommendations for designing sampling schemes
- Demonstrate proficiency in the use of R for analysis of sample design data, for
  - estimating a mean
  - estimating a change in mean
  - choosing sample sizes
- Demonstrate proficiency in the use of R to generate sampling designs
]





---
## Learning Outcomes

At the end of this Topic, students should be able to:

.pull-left[
- Calculate means and their uncertainty for a
  - simple random design
  - stratified random design
- **Make simple recommendations for designing sampling schemes**
- Demonstrate proficiency in the use of R for analysis of sample design data, for
  - estimating a mean
  - estimating a change in mean
  - choosing sample sizes
- Demonstrate proficiency in the use of R to generate sampling designs
]






---
## Learning Outcomes

At the end of this Topic, students should be able to:

.pull-left[
- Calculate means and their uncertainty for a
  - simple random design
  - stratified random design
- Make simple recommendations for designing sampling schemes
- **Demonstrate proficiency in the use of R for analysis of sample design data, for**
  - **estimating a mean**
  - **estimating a change in mean**
  - **choosing sample sizes**
- Demonstrate proficiency in the use of R to generate sampling designs
]





---
## Learning Outcomes

At the end of this Topic, students should be able to:

.pull-left[
- Calculate means and their uncertainty for a
  - simple random design
  - stratified random design
- Make simple recommendations for designing sampling schemes
- Demonstrate proficiency in the use of R for analysis of sample design data, for
  - estimating a mean
  - estimating a change in mean
  - choosing sample sizes
- **Demonstrate proficiency in the use of R to generate sampling designs**
]



